\section{Evaluation}
\label{sec:evaluation}

The evaluation is generated from repository scripts and processed CSVs; the paper-number audit rejects numeric claims that do not appear in generated evidence. The core full-RTL ledger reports \rcFullReplayPass/\rcFullReplayTotal\ compiler-backed record/replay PASS rows. The negative ledger rejects \rcNegativeReject\ replay-critical corruptions, reports \rcNegativeUnexpectedAccept\ unexpected accepts, and leaves \rcNegativeNA\ not-applicable rows for corruption classes outside the current commit-index harness.

\subsection{Replay, Scale, and Buffers}

Replay succeeds on the fixed compiler-backed suite in the full-RTL harness, but scaling is constrained by capsule capacity. The regenerated workload-scaling evidence reports 375/375 PASS rows with workload-aware v1 depths: 256 for smoke and short workloads, 1024 for medium, 4096 for long, and 16384 for stress. The buffer-sensitivity table shows replay success reaches 100.000000\% for each workload class at those selected depths, while the sticky overflow bit remains asserted on long-running fixed and no-failure rows that do not freeze at a property failure. The paper therefore treats buffer depth as a design parameter, not a hidden constant.

Capsule-size comparisons use the buffer depth required for the workload class under test. \texttt{capsule\_baseline\_summary.csv} reports median ReplayCapsule reductions versus the raw full instruction trace estimate of 59.52\% for smoke, 78.71\% for short, 83.18\% for medium, 64.86\% for long, and 22.84\% for stress. The measured v2 baseline summary adds a harder stress-row comparison: full instruction traces have median \rcVTwoStressFullInstructionBytes\ bytes and full commit traces have median \rcVTwoStressFullCommitBytes\ bytes, while the v2 core and hashed capsule rows have median \rcVTwoStressCoreBytes\ and \rcVTwoStressHashedBytes\ bytes. The same CSV includes a labeled \texttt{riscv\_etrace\_branch\_trace\_estimate} row; that estimate is smaller than ReplayCapsule-RV for these workloads, so the raw instruction trace comparison is a weak baseline, not a state-of-the-art trace-compression claim.

The v2 evidence package adds compressed recorder configurations and \rcExpandedBenchmarks\ expanded firmware families covering commanded actuator limits, late configuration sequencing, sensor debouncing, clear-on-read command/status behavior, alternate-MMIO-profile command/configuration cases, and realistic environmental-controller/power-rail control cases. The expanded replay ledger reports \rcExpandedReplayPass/\rcExpandedReplayTotal\ PASS rows across core, hashed, and full recorder configurations with an RTL capsule source and RTL-driven MMIO/IRQ replay stimulus. The self-replay handoff ledger further reports \rcSelfReplayPass/\rcSelfReplayTotal\ replay-mode-controller rows across the base and expanded benchmark families, showing that replay-critical words captured during record can drive same-instance replay without harness-preloaded capsule words. These rows improve workload and platform-profile coverage for the scoped model, but they do not replace the Verilator reset orchestration or memory/peripheral shell with a standalone board/silicon flow.

\subsection{Cost and Mapping}

The mapped FPGA results are same-target bring-up/debug measurements. The board-level baseline and ReplayCapsule wrappers use the same \rcMappedTarget\ target and \rcMappedFlow\ flow. After gating unselected v2 recorder instances in v1 mapped builds, the representative mapped-scaling summary reports LUT overhead from 114.20\% to 221.23\%, FF overhead from 174.53\% to 646.43\%, BRAM overhead of 0.00\%, and Fmax change from -19.56\% to -9.98\%.

For the selected v2 minimal recorder profile, the same-target ECP5 measured row reports +8.26\% LUT, +3.77\% FF, +0.00\% BRAM, and -0.04\% Fmax. The core and hashed v2 rows remain diagnostic-rich comparison points, with +68.00\% and +67.69\% LUT overhead and +81.49\% FF overhead. These rows support the design direction that replay-critical boundary-event capture should be separated from optional on-chip diagnostics.

The artifact also adds a Nangate45 ASIC/open-PDK lane. The Yosys+ABC synthesis-only rows report baseline cell area of 51157.652 square micrometers and selected v2 minimal area of 52058.062 square micrometers, or +1.76\%. The OpenROAD physical-flow rows place the same baseline and v2 configurations and run global routing with parsed area, WNS/TNS, and power. Baseline and selected v2 minimal report 53453.000 and 54374.000 square micrometers, respectively, both with 0.000 ns WNS and 5.990000 mW versus 6.590000 mW total power. These rows are global-routed implementation evidence, not detailed-route signoff or silicon energy data.

This overhead is acceptable only under the intended use case: temporary validation and post-failure replay instrumentation during hardware/software bring-up. It is not presented as a production always-on block. FPGA and Nangate45 results should be read as feasibility and cost-shape evidence rather than signoff implementation data.

\ifrcfullartifactpaper
\input{sections/generated_tables}
\fi
