\section{Limitations}

The scope is single-hart RV32I firmware with deterministic core semantics, the same program image, the same initial architectural state, and modeled external events. The current theorem excludes multicore interleavings, DMA unless modeled, cache/coherence effects unless modeled, analog nondeterminism, and claims about undefined C behavior.

MMIO side effects are modeled only at the replay-visible boundary. Interrupts are injected at an architectural boundary. Replay consumes every required event exactly once; missing, duplicate, reordered, or corrupted events must fail comparison. Capsule overflow invalidates replay availability for failure reconstruction unless the replay-critical prefix is still complete.

The v2 replay-consume path now includes same-instance self-replay rows that stream from the captured RTL store without harness-preloaded capsule words, and an RTL replay-mode controller now sequences captured-store arming and replay start. The path is still orchestrated by the Verilator harness for reset control and the memory/peripheral shell. The v2 full-core simulation path includes a synthesizable capture/source path and consumer: the record path exercises reset-persistent capture of replay-critical words, the source streams capsule words, and the consumer drives core-facing MMIO read data and IRQ replay. The design does not yet include a standalone board/silicon replay flow. The v1 workload evidence recovers 375/375 replay PASS rows only by using workload-aware depths: 256 for smoke and short, 1024 for medium, 4096 for long, and 16384 for stress. These depths increase capsule bytes and reduce the median stress-workload reduction versus a raw full-instruction trace to 22.84\%. High FF/LUT overhead remains an optimization target for diagnostic-rich configurations: same-target ECP5 overhead is still as high as 221.23\% LUT and 646.43\% FF in the broader mapped-scaling rows, and the v2 core/hashed diagnostic rows remain at +68.00\%/+67.69\% LUT and +81.49\% FF. The selected v2 minimal recorder profile is measured separately. Nangate45 ASIC rows use OpenROAD placement and global routing with parsed timing and power, but they are not detailed-route signoff, tapeout, silicon, or energy measurements. The evaluation is single-hart RV32I and does not cover multicore, DMA, caches/coherence, or arbitrary peripherals.

ReplayCapsule-RV v2 reduces the architectural risk by adding compressed recorder RTL, an RTL capsule capture/source path, a replay-mode controller, and a synthesizable replay-consume controller. The controllers have tested stream consumption, order checking, MMIO/interrupt checking, payload-hash rejection, saved-capsule full-core checks, and controller-driven captured-store self-replay checks across the measured v2 rows. The replay consumer also maps as a standalone ECP5 block. These rows should not be used to claim a standalone board/silicon replay engine, because reset orchestration and the memory/peripheral shell remain in the harness.
