\section{Record/Replay Implementation}

The replay comparator consumes an expected capsule and an observed replay trace. A passing comparison requires matching property metadata, the required event classes at the selected commit or cycle index, exact payload equality for replay-driving events, and no extra replay-driving events. Negative tests corrupt metadata, remove events, duplicate events, shift indices, swap order tags, and perturb payloads. The same comparator is used for model fixtures and exported RTL-smoke capsules.

The current replay-consume path is hardware-driven at the capsule stream and MMIO/IRQ boundaries. The saved-capsule replay ledger records a capsule from the instrumented PicoRV32 wrapper, reruns the same compiler-backed firmware under replay control, preloads the replay-critical capsule words into an RTL capsule source, and checks the resulting trace. The self-replay ledger exercises the stronger handoff: the same Verilator instance records replay-critical words into the RTL capture store, resets the core while retaining that store, and uses an RTL replay-mode controller to launch replay from the captured store without harness-preloaded capsule words. During v2 replay, the host no longer streams capsule words cycle by cycle and no longer computes replay MMIO values or IRQ timing; the RTL replay-mode controller selects the captured source, the RTL source streams capsule words into the RTL consumer, and the consumer validates the observed event sequence while driving core-facing MMIO read data and IRQ replay through the PicoRV32 wrapper. This is stronger evidence for full-core replay plumbing, but it is not a standalone replay engine because reset orchestration and the memory/peripheral shell remain in the Verilator harness.

Bounded local checks cover recorder and control contracts such as event classification, buffer behavior, property signatures, replay mismatch handling, register access, hash/signature update, and MMIO/interrupt logging. These checks support local RTL obligations; they are not a mechanized end-to-end processor theorem.
